Supplementary Materials- A Bayesian networks approach to infer social changes from burials in northeastern Taiwan during the European colonization period

### 2021-08-24 analysis/paper/supplementary-material.Rmd
note of code for fig 3 & 4 in the SI

```{r pre-diag-plots, include= FALSE}
# get the first set of diagnostic plots
x <- pre_bergm

@@

```{r post-diag-plots, include= FALSE}
# get the first set of diagnostic plots
y <- post_bergm

@@

```{r figure-pre-diag, fig.cap = "MCMC output of the pre-European model. In the order of edges, nodematch-age, nodematch-sex, nodematch-ritual, nodematch-value, gwesp, gwdeg, and dyadcov.distance."}
knitr::include_graphics(here::here("analysis", "figures", "008-pre-diag.png"))
```

```{r figure-post-diag, fig.cap = "MCMC output of the post-European model. In the order of edges, nodematch-age, nodematch-sex, nodematch-ritual, nodematch-value, gwesp, gwdeg, and dyadcov.distance."}
knitr::include_graphics(here::here("analysis", "figures", "009-post-diag.png"))
```

>>>>

```{r pre-diag-plots, include= FALSE}
# Figure 1 in the SI
# get the first set of diagnostic plots
x <- pre_bergm

@@

```{r post-diag-plots, include= FALSE}
# Figure 2 in the SI
# get the first set of diagnostic plots
y <- post_bergm

@@

```{r figure-pre-diag, fig.cap = "MCMC output of the pre-European model. In the order of edges, nodematch-age, nodematch-sex, nodematch-ritual, nodematch-value, gwesp, gwdeg, and dyadcov.distance."}
# Figure 3 in the SI (code is in 007-bgof-assessment-vis.R)
knitr::include_graphics(here::here("analysis", "figures", "008-pre-diag.png"))
```

```{r figure-post-diag, fig.cap = "MCMC output of the post-European model. In the order of edges, nodematch-age, nodematch-sex, nodematch-ritual, nodematch-value, gwesp, gwdeg, and dyadcov.distance."}
# Figure 4 in the SI (code is in 007-bgof-assessment-vis.R)
knitr::include_graphics(here::here("analysis", "figures", "009-post-diag.png"))
```
